### 2018-04-04 paper.Rmd

One common use of the CHILDES corpora is estimating the frequency with which children hear different words. These frequency estimates are used both in the development of theory (e.g. frequent words are learned earlier; @goodman2008), and in the construction of age-appropriate experimental stimuli. One benefit of the childes-db interface is that it allows for easy analysis of how the frequency of words changes over development. Many of our theories in which children learn the structure of language from its statistical properties implicitly assume that these statistics are *stationary*, i.e. unchanging over development (e.g., @saffran1996). However a number of recent analysis show that the frequencies with which infants encounter both linguistic and visual properties of their environment may change dramattically over development [@fausey2016], and these changing distributions may produce similarly dramatic changes in the ease or difficulty with which these regularities can be learned [@elman1993].

To demonstrate how one might discover such a non-staionarity, we take as a case study the frequency with which children hear the color words of English (e.g. "blue", "green"). Color words tend to be learned relatively late by children, potentially in part due to the abstractness of the meanings to which they refer (see @wagner2013). However, within the set of color words, the frequency with which these words are heard predicts a significant fraction of the variance in their order of acquisition [@yurovsky2015]. But are these frequencies stationary--e.g. do children hear "blue" as often at 12 months as they do at 24 months? We answer this question in two ways--first using the childesb shiny apps, and then using the `childesr` package.

```{r}
colors <- c("black", "white", "red", "green", "yellow", "blue", "brown", 
             "orange", "pink", "purple")

>>>>

One common use of the CHILDES corpora is estimating the frequency with which children hear different words. These frequency estimates are used both in the development of theory [e.g. frequent words are learned earlier; @goodman2008], and in the construction of age-appropriate experimental stimuli. One benefit of the `childesdb` interface is that it allows for easy analysis of how the frequencies of words change over development. Many of our theories in which children learn the structure of language from its statistical properties implicitly assume that these statistics are *stationary*, i.e. unchanging over development [e.g., @saffran1996]. However a number of recent analysis show that the frequencies with which infants encounter both linguistic and visual properties of their environment may change dramatically over development [@fausey2016], and these changing distributions may produce similarly dramatic changes in the ease or difficulty with which these regularities can be learned [@elman1993].

To demonstrate how one might discover such a non-stationary, we take as a case study the frequency with which children hear the color words of English (e.g. "blue", "green"). Color words tend to be learned relatively late by children, potentially in part due to the abstractness of the meanings to which they refer [see @wagner2013]. However, within the set of color words, the frequency with which these words are heard predicts a significant fraction of the variance in their order of acquisition [@yurovsky2015]. But are these frequencies stationary--e.g. do children hear "blue" as often at 12 months as they do at 24 months? We answer this question in two ways--first using the childesb shiny apps, and then using the `childesr` package.

#### Using shiny

To investigate whether the frequency of color words is stationary over development, a user can navigate to the Frequency app, and enter a set of color words into the `Word` selector separated by a comma: here "blue, red, green." Because the question of interest is about the frequency of words in the input (rather than produced by children), the `Speaker` field can be set to reflect this. In this example we select "Mother" because, across corpora in CHIDLES, the speaker tagged with the Mother role tends to produce most of the words that children hear. Because children learn most of their basic color words by the age of 5, the age range 1-5 years is a reaonable choice for `Ages to include`. The results of these selections are shown in Figure \ref{fig:color-shiny}. We can also create a hyperlink to store these set of choices so that we can share these results with others, or with ourselves in the future, byby clicking on the `Bookmark` button in the bottom left corner.

From this figure, it seems likely that children hear "blue" more frequently early in development, but the trajectories of the "red" and "green" are less clear. We also do not have a good sense of the errors of these measurements, are limited to just a few colors at a time before the plot becomes too busy, and cannot combine frequencies across speakers. To perform this analysis in a more compelling and complete way, a user can use the `childesr` interface to get more direct access to the CHILDES corpora.

```{r color-shiny, fig.width = 10, fig.height = 6, fig.cap = "An example of using the Frequency shiny app to explore how children's color input changes over development"}
knitr::include_graphics("images/color-shiny.png")
```

#### Using childesr

Figure \ref{fig:color-plot}.

```{r color-plot, fig.height = 5, fig.width = 10, fig.cap ="Color frequency as a function of age. Points represent means across transcripts, error bars represent 95% confidence intervals computed by nonparametric bootstrap", cache = TRUE, message = FALSE, warning = FALSE}
colors <- c("black", "white", "red", "green", "yellow", "blue", "brown", 
             "orange", "pink", "purple")
